Weight-adjusted discontinuous Galerkin methods: matrix-valued weights and elastic wave propagation in heterogeneous media

### 2017-01-17 docs/elasticity_notes/main.tex
adding old elas files + some euler experiments

\usepackage{fullpage}
\usepackage{hyperref}
%\let\proof\relax
%\let\endproof\relax
\usepackage{amsmath,amssymb,amsfonts,mathrsfs}%,amsthm}
\usepackage[titletoc,toc,title]{appendix}

%\usepackage{lineno}
\usepackage{array} 
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{mathtools}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{bm}
%\usepackage{tikz}
\usepackage[normalem]{ulem}
\usepackage{hhline}

@@

\usepackage{pgfplots}
\usepackage{pgfplotstable}
\definecolor{markercolor}{RGB}{124.9, 255, 160.65}
\pgfplotsset{width=10cm,compat=1.9}
\pgfplotsset{
tick label style={font=\small},
label style={font=\small},
legend style={font=\small}
}

@@

In general anisotropic media, $\bm{C}$ is symmetric and positive-definite.  For two-dimensional isotropic media, $\bm{C}$ is given as
\[
\bm{C}= \LRp{
\begin{array}{ccc}
2\mu+\lambda  &  \lambda  &     0\\
\lambda &       2\mu+\lambda &      0\\
          0 &      0           &     {\mu}
\end{array}}, 
\]
where $\lambda,\mu$ are Lame parameters.  For three-dimensional isotropic media, $\bm{C}$ is given instead by
\[
%\bm{C}= 
%\LRp{
%\begin{array}{cccccc}
%2\mu+\lambda  &  \lambda  &     \lambda  & & & \\
%\lambda &   2\mu+\lambda & \lambda   & & & \\
%\lambda & \lambda &   2\mu+\lambda &    & &\\
% &   &    & {\mu} & &\\
%&  &   &    & {\mu} &\\
%& &  &   &    & {\mu} \\
%\end{array}}.  
\LRp{\begin{array}{cccc}
2\mu+\lambda  &  \lambda  &     \lambda   & \\
\lambda &   2\mu+\lambda & \lambda   &  \\
\lambda & \lambda &   2\mu+\lambda &    \\
 &   &    & {\mu}\bm{I}^{3\times3} \\
\end{array}}.  
\]
We will consider both spatially varying isotropic and anisotropic media in this work.

@@

We can now specify a DG formulation for the linear elastic wave equation (\ref{eq:symelas}).  Symmetric hyperbolic systems readily admit a DG formulation based on penalty fluxes \cite{chan2016short}.  For the linear elastic wave equation in symmetric first order form, this formulation is given as
\begin{align}
\sum_{D^k\in \Oh} \LRp{\rho \pd{\bm{v}}{t},\bm{w}}_{\Lk} &= 
\sum_{D^k\in \Oh} \LRp{\LRp{ \sum_{i=1}^d \bm{A}_i^T\pd{\bm{\sigma}}{\bm{x}_i} + \bm{f},\bm{w}}_{\Lk}  + \LRa{\frac{1}{2}\bm{A}_n^T\jump{\bm{\sigma}} + \frac{\tau_v}{2}\bm{A}_n^T\bm{A}_n\jump{\bm{v}},\bm{w}}_{\Ldk}} \nonumber\\
\sum_{D^k\in \Oh}\LRp{\bm{C}^{-1} \pd{\bm{\sigma}}{t},\bm{q}}_{\Lk} &=
\sum_{D^k\in \Oh}\LRp{\LRp{\sum_{i=1}^d \bm{A}_i \pd{\bm{v}}{\bm{x}_i},\bm{q}}_{\Lk} + \LRa{\frac{1}{2}\bm{A}_n\jump{\bm{v}} + \frac{\tau_{\sigma}}{2}\bm{A}_n\bm{A}_n^T\jump{\bm{\sigma}},\bm{q}}_{\Ldk}},
\label{eq:dgform}
\end{align}
for all $\bm{w},\bm{q}\in V_h\LRp{\Omega_h}$.  Here, $\tau_v,\tau_\sigma \geq 0$ are penalty parameters and $\bm{A}_n$ is the normal matrix defined on a face $f$ as $\bm{A}_n = \sum_{i=1}^d \bm{n}_i \bm{A}_i$.  In two dimensions, $\bm{A}_n$ is 
\[
\bm{A}_n =  \LRp{\begin{array}{cc}
{n}_x & 0\\
 0 & {n}_y\\
{n}_y & {n}_x
\end{array}}.
\]
while in three dimensions, $\bm{A}_n$ is
\[
\bm{A}_n =  \LRp{\begin{array}{ccc}
{n}_x & 0 & 0\\
 0 & {n}_y & 0\\
0&  0 & {n}_z \\
0 &{n}_z & {n}_y\\
{n}_z & 0 & {n}_x\\
{n}_y & {n}_x & 0\\
\end{array}}.  
\]

@@

Let $\bm{U},\bm{U}_h$ denote the exact and discrete WADG solutions, respectively.  We will assume that $\bm{U},\pd{\bm{U}}{t}$ are sufficiently regular such that
\[
\nor{\bm{U}}_{W^{N+1,2}\LRp{\Oh}}} < \infty, \qquad \nor{\pd{\bm{U}}{t}}_{W^{N+1,2}\LRp{\Oh}} < \infty,
\]
where we define $\nor{\bm{U}}_{W^{N+1,2}\LRp{\Oh}}}^2 = \sum_k \nor{\bm{U}}_{W^{N+1,2}\LRp{D^k}}}^2$.

@@

The right hand side term involving $\bm{\epsilon}$ can be bounded using interpolation estimates and a standard $hp$ trace inequality $\nor{u}_{\Ldk} \leq Ch^{-1/2} \nor{u}_{\Lk}$ \cite{warburton2003constants,chan2015gpu} 

@@

We apply this estimate and eliminate factors of $b(\bm{\eta},\bm{\eta})$ on both sides.  Then, integrating from $[0,T]$ and using Lemma~\ref{lemma:props} yields
A_{\min}^2 \nor{\bm{\eta}}^2_{\L} \leq \int_0^T \nor{\pd{\bm{\delta}}{t}}_{\L} \nor{\bm{\eta}}_{\L} + C h^{2N+1} \nor{\bm{U}}^2_{W^{N+1,2}(\Omega)}.
%where $C$ depends on $\tau_v,\tau_\sigma, N$, and 
where $A_{\min} =\min\LRp{ \rho_{\min}, \tilde{c}_{\min}}$.  Since $\bm{A}_0$ is independent of $t$, Theorem~\ref{thm:west} gives

@@

where $A_{\max} = \max\LRp{\frac{\rho_{\max}}{\rho_{\min}}, c_{\max} \tilde{c}_{\max}}$.  
Using this estimate and Young's inequality on $\nor{\pd{\bm{\delta}}{t}}_{\L} \nor{\bm{\eta}}_{\L}$ gives
\nor{\bm{\eta}}_{\L}^2 \leq \int_0^T \nor{\bm{\eta}}^2_{\L} + C\LRp{h^{2N+2} \LRp{\frac{A_{\max}}{A_{\min}}}^2\nor{\bm{A}_0}_{W^{N+1,\infty}(\Oh)}^2\nor{\pd{\bm{U}}{t}}_{\L}^2  + h^{2N+1} \nor{\bm{U}}^2_{W^{N+1,2}(\Oh)}}.
An application of Gronwall's inequality \cite{riviere2008discontinuous} and the arithmetic-geometric mean inequality then gives 
\nor{\bm{\eta}}_{\L} \leq C e^{T} h^{N+1/2} \sup_{t \in [0,T]}\LRp{h^{1/2} \LRp{\frac{A_{\max}}{A_{\min}}}\nor{\bm{A}_0}_{W^{N+1,\infty}(\Oh)}\nor{\pd{\bm{U}}{t}}_{\L}  +  \nor{\bm{U}}_{W^{N+1,2}(\Oh)}}.

@@

\nor{\bm{U}-\bm{U}_h} \leq C\LRp{1 + e^{T}} h^{N + 1/2}\sup_{t \in [0,T]}\LRp{ h^{1/2}C_A\nor{\pd{\bm{U}}{t}}_{W^{N+1,2}(\Oh)}+\nor{\bm{U}}_{W^{N+1,2}(\Oh)}}.

@@

where $C_A = \LRp{\frac{A_{\max}}{A_{\min}}}\nor{\bm{A}_0}_{W^{N+1,\infty}(\Oh)}$.

@@

\begin{figure}
\centering
\subfloat[$\tau_v = \tau_\sigma = 0$]{\includegraphics[width=.475\textwidth]{../figs/spectra_tau0.png}}
%\hspace{1em}
\subfloat[$\tau_v = \tau_\sigma = 1$]{\includegraphics[width=.475\textwidth]{../figs/spectra_tau1.png}}
\caption{Spectra for $N=4$ and $h = 1/4$, using randomly chosen $\bm{C}(\bm{x})$ with eigenvalues between $[d_{\min}, 1]$ at each quadrature point.  For both $\tau_v = \tau_\sigma = 0$ and $\tau_v = \tau_\sigma = 1$, the largest real part of the spectra is $O(10^{-14})$.}
\label{fig:spectra}
\end{figure}

@@

\begin{figure}
\centering
\subfloat[$\LRb{\bm{\sigma}_{xx}+\bm{\sigma}_{yy}}$]{\includegraphics[width=.475\textwidth]{../figs/inclusion_aligned.png}}
\hspace{2em}
\subfloat[$\LRb{\bm{\sigma}_{xy}}$]{\includegraphics[width=.475\textwidth]{../figs/inclusion_aligned_shear.png}}
%\subfloat[Aligned mesh (zoom)]{\includegraphics[height=.24\textwidth]{../figs/inclusion_aligned_zoom.png}}
%\\
%\subfloat[Un-aligned mesh]{\includegraphics[height=.24\textwidth]{../figs/inclusion_unaligned.png}}
%\hspace{2em}
%\subfloat[Un-aligned mesh (zoom)]{\includegraphics[height=.24\textwidth]{../figs/inclusion_unaligned_zoom.png}}
\caption{Values of different solution fields at $T=.4$ for the stiff inclusion problem of Leveque \cite{leveque2002finite} with order of approximation $N=5$.}
\label{fig:incl}
\end{figure}

@@

The computational domain is taken to be $[-.32, .32]^2$, and following \cite{komatitsch2000simulation,de2007arbitrary}, we use $N=5$ and a triangular mesh of $32768$ elements constructed by subdividing a grid of $128\times 128$ uniform quadrilaterals.  This mesh corresponds to an element size of $.005$, as used in \cite{komatitsch2000simulation,de2007arbitrary}.  Forcing is applied to the $y$-component of the velocity by a Ricker wavelet point source 
\[
f(\bm{x},t) = \LRp{1 - 2(\pi f_0 (t-t_0))^2} e^{-(\pi f_0 (t-t_0))^2}\delta(x-x_0),
\]
where $x_0 = -.02$, $f_0 = .17$, and $t_0 = 1/f_0$.\footnote{All values and units are adapted from \cite{komatitsch2000simulation,de2007arbitrary}, and correspond to units of meters, kg, and microseconds.}  The penalty parameters are taken to be $\tau_\rho = \tau_\sigma = 1/2$.  Figure~\ref{fig:aniso} shows the $y$-component of velocity $\bm{v}_2$ at times $T = 30 \mu s$ (zoomed in) and $T= 60 \mu s$.  Both results show qualitative agreement with reference results from \cite{carcione1988wave,komatitsch2000simulation,de2007arbitrary}.  
\begin{figure}
\centering
%\subfloat[$\bm{v}_1$]{\includegraphics[width=.45\textwidth]{}}
%\subfloat[$\bm{v}_2$]{\includegraphics[width=.45\textwidth]{}}
\subfloat[$T=30 \mu s$ (zoomed in)]{\includegraphics[height=18em]{../figs/aniso1.png}}
\hspace{3em}
\subfloat[$T=60 \mu s$]{\includegraphics[height=18.25em]{../figs/aniso2.png}}
\caption{An example of wave propagation in heterogeneous anisotropic media.  The vertical component of the velocity $\bm{v}_2$ is shown at $T = 30$ and $T=60$ microseconds. }
\label{fig:aniso}
\end{figure}

@@

Finally, we present a three-dimensional example of elastic wave propagation in heterogeneous media with sub-element variations and a discontinuity across an interface.  We consider isotropic elastic wave propagation on the cube $[-.5,.5]^3$ with a discontinuity in material coefficients across $z = 0$
\[
\rho = 1, \qquad \mu(\bm{x}) = \begin{cases}
2 + w(\bm{x}), & z < 0\\
1 + w(\bm{x}), & z > 0
\end{cases},
\qquad
\lambda(\bm{x}) = \begin{cases}
2, & z < 0\\
1, & z > 0
\end{cases}
\]
where $w(\bm{x})$ is a spatially varying weight.  
%isotropic media for $z < 0$ and a transversely isotropic media for $z > 0$.  For isotropic media, we take $\mu(\bm{x}) = w(\bm{x})$ and $\lambda(\bm{x}) = 2w(\bm{x})$, where $w(\bm{x})$ is a spatially varying weight function to be specified.  For $z > 0$, we take $\bm{C}$ to be 
%\[
%\bm{C} &= w(\bm{x}) \LRp{
%\begin{array}{cccccc}
%c_{11} & c_{12} & \lambda & & &\\
%c_{12} & c_{11} & \lambda & & &\\
%\lambda & \lambda & 2\mu+\lambda & & &\\
%& & & \mu & &\\
%& & & & \mu &\\
%& & & & & (c_{11}-c_{12})/2\\
%\end{array}
%}
%\]
%with $c_{11} = 1$ and $c_{12} = .5$.  
Forcing is applied to the $x$-component of velocity through a smoothed point source and Ricker wavelet
\[
f(\bm{x},t) = \LRp{1 - 2(\pi f_0 (t-t_0))^2} e^{-(\pi f_0 (t-t_0))^2}e^{- \LRp{a \nor{\bm{x}-\bm{x}_0}}^2}
\]
where $\bm{x}_0 = (0,0,.1)^T$, $a = 100$, $f_0 = 10$, and $t_0 = 1/f_0$.  
\begin{figure}
\centering
\subfloat[Computational mesh]{\includegraphics[width=.28\textwidth]{../figs/cubeSplitFine.png}\label{subfig:mesh}}
\hspace{.5em}
\subfloat[$w(\bm{x}) = 0$]{\includegraphics[width=.35\textwidth]{../figs/pplane0.png}}
%\hspace{.25em}
\subfloat[$w(\bm{x})  = .5 \cos(3\pi x)\cos(3\pi y)\cos(3\pi z) $]{\includegraphics[width=.35\textwidth]{../figs/pplanew0.png}}
\caption{Mesh and $xz$, $xy$ slices of $\bm{v}_1$ at $T = .5$.  The order of approximation is taken to be $N=5$.  }
\label{fig:3d}
\end{figure}
Figure~\ref{fig:3d} shows the $x$-velocity of the computed solution at $T = .5$ with
\[
w(\bm{x}) = .5 \cos(3\pi x)\cos(3\pi y)\cos(3\pi z), 
\]  
as well as $w(\bm{x}) = 0$ for reference.  Figure~\ref{subfig:mesh} shows the unstructured mesh of 222824 tetrahedral elements of degree $N=5$ used to compute both solutions.

@@

We note that the implementation of this method reduces to the application of the weight-adjusted mass matrix inverse and the evaluation of constant-coefficient terms in the DG formulation.  The cost of the latter step can be reduced (especially at high orders of approximation) by using fast methods based on Bernstein-Bezier bases for the application of derivative and lift matrices for constant-coefficient terms \cite{chan2015bbdg}.  Finally, the approach presented here is more generally applicable to problems involving a weighted mass matrix with a matrix-valued weight, which we will explore in the future.  These include hyperbolic systems of PDEs with a right hand side of the form $\bm{A}_{0}(\bm{x})\pd{\bm{U}}{t}$, such as Maxwell's equations for cloaking problems \cite{li2012time}.

>>>>

\usepackage{fullpage}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage[titletoc,toc,title]{appendix}

\usepackage{array} 
\usepackage{listings}
\usepackage{mathtools}
\usepackage{pdfpages}
\usepackage[textsize=footnotesize,color=green]{todonotes}
\usepackage{bm}
%\usepackage{tikz}
\usepackage[normalem]{ulem}
\usepackage{hhline}

@@

\usepackage{pgfplots}
\usepackage{pgfplotstable}
\definecolor{markercolor}{RGB}{124.9, 255, 160.65}
\pgfplotsset{width=10cm,compat=1.3}
\pgfplotsset{
tick label style={font=\small},
label style={font=\small},
legend style={font=\small}
}

@@

In general anisotropic media, $\bm{C}$ is symmetric and positive-definite.  For two-dimensional isotropic media, $\bm{C}$ is given as
\[
\bm{C}= \LRp{
\begin{array}{ccc}
2\mu+\lambda  &  \lambda  &     0\\
\lambda &       2\mu+\lambda &      0\\
0 & 0 & \mu
\end{array}}, 
\]
where $\lambda,\mu$ are Lame parameters.  For three-dimensional isotropic media, $\bm{C}$ is given instead by
\[
\LRp{\begin{array}{cccc}
2\mu+\lambda  &  \lambda  &     \lambda   & \\
\lambda &   2\mu+\lambda & \lambda   &  \\
\lambda & \lambda &   2\mu+\lambda &    \\
 &   &    & {\mu}\bm{I}^{3\times3} \\
\end{array}}.  
\]
We will consider both spatially varying isotropic and anisotropic media in this work.

@@

We can now specify a DG formulation for the linear elastic wave equation (\ref{eq:symelas}).  Symmetric hyperbolic systems readily admit a DG formulation based on penalty fluxes \cite{chan2016short}.  For the linear elastic wave equation in symmetric first order form, this formulation is given as
\begin{align}
&\sum_{D^k\in \Oh} \LRp{\rho \pd{\bm{v}}{t},\bm{w}}_{\Lk} = \sum_{D^k\in \Oh} \LRp{\LRp{ \sum_{i=1}^d \bm{A}_i^T\pd{\bm{\sigma}}{\bm{x}_i} + \bm{f},\bm{w}}_{\Lk}  + \LRa{\frac{1}{2}\bm{A}_n^T\jump{\bm{\sigma}} + \frac{\tau_v}{2}\bm{A}_n^T\bm{A}_n\jump{\bm{v}},\bm{w}}_{\Ldk}} \nonumber\\
&\sum_{D^k\in \Oh} \LRp{\bm{C}^{-1} \pd{\bm{\sigma}}{t},\bm{q}}_{\Lk} = \sum_{D^k\in \Oh}\LRp{\LRp{\sum_{i=1}^d \bm{A}_i \pd{\bm{v}}{\bm{x}_i},\bm{q}}_{\Lk} + \LRa{\frac{1}{2}\bm{A}_n\jump{\bm{v}} + \frac{\tau_{\sigma}}{2}\bm{A}_n\bm{A}_n^T\jump{\bm{\sigma}},\bm{q}}_{\Ldk}},
\label{eq:dgform}
\end{align}
for all $\bm{w},\bm{q}\in V_h\LRp{\Omega_h}$.  Here, $\tau_v,\tau_\sigma \geq 0$ are penalty parameters and $\bm{A}_n$ is the normal matrix defined on a face $f$ as $\bm{A}_n = \sum_{i=1}^d \bm{n}_i \bm{A}_i$.  In two dimensions, $\bm{A}_n$ is 
\[
\bm{A}_n =  \LRp{\begin{array}{cc}
{n}_x & 0\\
 0 & {n}_y\\
{n}_y & {n}_x
\end{array}}.
\]
while in three dimensions, $\bm{A}_n$ is
\[
\bm{A}_n =  \LRp{\begin{array}{ccc}
{n}_x & 0 & 0\\
 0 & {n}_y & 0\\
0&  0 & {n}_z \\
0 &{n}_z & {n}_y\\
{n}_z & 0 & {n}_x\\
{n}_y & {n}_x & 0\\
\end{array}}.  
\]

@@

Let $\bm{U},\bm{U}_h$ denote the exact and discrete WADG solutions, respectively.  We will assume that $\bm{U},\pd{\bm{U}}{t}$ are sufficiently regular such that
\[
\nor{\bm{U}}_{W^{N+1,2}\LRp{\Oh}} < \infty, \qquad \nor{\pd{\bm{U}}{t}}_{W^{N+1,2}\LRp{\Oh}} < \infty,
\]
where we define $\nor{\bm{U}}_{W^{N+1,2}\LRp{\Oh}}^2 = \sum_k \nor{\bm{U}}_{W^{N+1,2}\LRp{D^k}}^2$.

@@

We eliminate factors of $b(\bm{\eta},\bm{\eta})$ on both sides and bound right hand side terms.  The trace term is bounded using a standard $hp$ trace inequality \cite{warburton2003constants} and an interpolation estimate

@@

Since $\bm{A}_0$ is independent of $t$, Theorem~\ref{thm:west} gives

@@

where $A_{\max} = \max\LRp{\frac{\rho_{\max}}{\rho_{\min}}, c_{\max} \tilde{c}_{\max}}$.  Then, integrating from $[0,T]$ and using Lemma~\ref{lemma:props} yields 
A_{\min} \nor{\bm{\eta}}^2_{\L} \leq C\int_0^T  h^{N+1}A_{\max}\nor{\bm{A}_0}_{W^{N+1,\infty}(\Oh)}\nor{\pd{\bm{U}}{t}}_{\L} \nor{\bm{\eta}}_{\L} + h^{2N+1} \nor{\bm{U}}^2_{W^{N+1,2}(\Omega)}.
where $A_{\min} =\min\LRp{ \rho_{\min}, \tilde{c}_{\min}}$.  Applying the modified Gronwall's inequality (Lemma 1.10 in \cite{dolejvsi2015discontinuous}; see also \cite{chan2016weight1}) to (\ref{eq:intermed}) then yields
\nor{\bm{\eta}}_{\L} &\leq \frac{1}{A_{\min}} \int_0^T CA_{\max} h^{N+1}\nor{\bm{A}_0}_{W^{N+1,\infty}(\Oh)}\nor{\pd{\bm{U}}{t}}_{\L} + \sup_{t\in [0,T]} \sqrt{\int_0^T C h^{2N+1} \nor{\bm{U}}^2_{W^{N+1,2}(\Omega)}}\\
&\leq \frac{C T h^{N+1/2}}{A_{\min}} \sup_{t \in [0,T]}\LRp{h^{1/2} A_{\max}\nor{\bm{A}_0}_{W^{N+1,\infty}(\Oh)}\nor{\pd{\bm{U}}{t}}_{\L}  +  \nor{\bm{U}}_{W^{N+1,2}(\Oh)}}.

@@

\nor{\bm{U}-\bm{U}_h} \leq \LRp{C_1 + C_2 T} h^{N + 1/2}\sup_{t \in [0,T]}\LRp{ h^{1/2}\nor{\bm{A}_0}_{W^{N+1,\infty}(\Oh)}\nor{\pd{\bm{U}}{t}}_{W^{N+1,2}(\Oh)}+\nor{\bm{U}}_{W^{N+1,2}(\Oh)}}.

@@

where $C_2$ depends on $A_{\min}, A_{\max}$.

@@

\begin{figure}
\centering
\subfloat[$\tau_v = \tau_\sigma = 0$]{\includegraphics[width=.475\textwidth]{figs/spectra_tau0.png}}
%\hspace{1em}
\subfloat[$\tau_v = \tau_\sigma = 1$]{\includegraphics[width=.475\textwidth]{figs/spectra_tau1.png}}
\caption{Spectra for $N=4$ and $h = 1/4$, using randomly chosen $\bm{C}(\bm{x})$ with eigenvalues between $[d_{\min}, 1]$ at each quadrature point.  For both $\tau_v = \tau_\sigma = 0$ and $\tau_v = \tau_\sigma = 1$, the largest real part of the spectra is $O(10^{-14})$.}
\label{fig:spectra}
\end{figure}

@@

\begin{figure}
\centering
\subfloat[$\LRb{\bm{\sigma}_{xx}+\bm{\sigma}_{yy}}$]{\includegraphics[width=.475\textwidth]{figs/inclusion_aligned.png}}
\hspace{2em}
\subfloat[$\LRb{\bm{\sigma}_{xy}}$]{\includegraphics[width=.475\textwidth]{figs/inclusion_aligned_shear.png}}
%\subfloat[Aligned mesh (zoom)]{\includegraphics[height=.24\textwidth]{figs/inclusion_aligned_zoom.png}}
%\\
%\subfloat[Un-aligned mesh]{\includegraphics[height=.24\textwidth]{figs/inclusion_unaligned.png}}
%\hspace{2em}
%\subfloat[Un-aligned mesh (zoom)]{\includegraphics[height=.24\textwidth]{figs/inclusion_unaligned_zoom.png}}
\caption{Values of different solution fields at $T=.4$ for the stiff inclusion problem of Leveque \cite{leveque2002finite} with order of approximation $N=5$.}
\label{fig:incl}
\end{figure}

@@

The computational domain is taken to be $[-.32, .32]^2$, and following \cite{komatitsch2000simulation,de2007arbitrary}, we use $N=5$ and a triangular mesh of $32768$ elements constructed by subdividing a grid of $128\times 128$ uniform quadrilaterals.  This mesh corresponds to an element size of $.005$, as used in \cite{komatitsch2000simulation,de2007arbitrary}.  Forcing is applied to the $y$-component of the velocity by a Ricker wavelet point source 
\[
f(\bm{x},t) = \LRp{1 - 2(\pi f_0 (t-t_0))^2} e^{-(\pi f_0 (t-t_0))^2}\delta(x-x_0),
\]
where $x_0 = -.02$, $f_0 = .17$, and $t_0 = 1/f_0$.\footnote{All values and units are adapted from \cite{komatitsch2000simulation,de2007arbitrary}, and correspond to units of meters, kg, and microseconds.}  The penalty parameters are taken to be $\tau_\rho = \tau_\sigma = 1/2$.  Figure~\ref{fig:aniso} shows the $y$-component of velocity $\bm{v}_2$ at times $T = 30 \mu s$ (zoomed in) and $T= 60 \mu s$.  Both results show qualitative agreement with reference results from \cite{carcione1988wave,komatitsch2000simulation,de2007arbitrary}.  
\begin{figure}
\centering
%\subfloat[$\bm{v}_1$]{\includegraphics[width=.45\textwidth]{}}
%\subfloat[$\bm{v}_2$]{\includegraphics[width=.45\textwidth]{}}
\subfloat[$T=30 \mu s$ (zoomed in)]{\includegraphics[height=18em]{figs/aniso1.png}}
\hspace{3em}
\subfloat[$T=60 \mu s$]{\includegraphics[height=18.25em]{figs/aniso2.png}}
\caption{An example of wave propagation in heterogeneous anisotropic media.  The vertical component of the velocity $\bm{v}_2$ is shown at $T = 30$ and $T=60$ microseconds. }
\label{fig:aniso}
\end{figure}

@@

Finally, we present a three-dimensional example of elastic wave propagation in heterogeneous media with sub-element variations and a discontinuity across an interface.  We consider isotropic elastic wave propagation on the cube $[-.5,.5]^3$ with a discontinuity in material coefficients across $z = 0$
\[
\rho = 1, \qquad \mu(\bm{x}) = \begin{cases}
2 + w(\bm{x}), & z < 0\\
1 + w(\bm{x}), & z > 0
\end{cases},
\qquad
\lambda(\bm{x}) = \begin{cases}
2, & z < 0\\
1, & z > 0
\end{cases}
\]
where $w(\bm{x})$ is a spatially varying weight.  
%isotropic media for $z < 0$ and a transversely isotropic media for $z > 0$.  For isotropic media, we take $\mu(\bm{x}) = w(\bm{x})$ and $\lambda(\bm{x}) = 2w(\bm{x})$, where $w(\bm{x})$ is a spatially varying weight function to be specified.  For $z > 0$, we take $\bm{C}$ to be 
%\[
%\bm{C} &= w(\bm{x}) \LRp{
%\begin{array}{cccccc}
%c_{11} & c_{12} & \lambda & & &\\
%c_{12} & c_{11} & \lambda & & &\\
%\lambda & \lambda & 2\mu+\lambda & & &\\
%& & & \mu & &\\
%& & & & \mu &\\
%& & & & & (c_{11}-c_{12})/2\\
%\end{array}
%}
%\]
%with $c_{11} = 1$ and $c_{12} = .5$.  
Forcing is applied to the $x$-component of velocity through a smoothed point source and Ricker wavelet
\[
f(\bm{x},t) = \LRp{1 - 2(\pi f_0 (t-t_0))^2} e^{-(\pi f_0 (t-t_0))^2}e^{- \LRp{a \nor{\bm{x}-\bm{x}_0}}^2}
\]
where $\bm{x}_0 = (0,0,.1)^T$, $a = 100$, $f_0 = 10$, and $t_0 = 1/f_0$.  
\begin{figure}
\centering
\subfloat[Computational mesh]{\includegraphics[width=.28\textwidth]{figs/cubeSplitFine.png}\label{subfig:mesh}}
\hspace{.5em}
\subfloat[$w(\bm{x}) = 0$]{\includegraphics[width=.35\textwidth]{figs/pplane0.png}}
%\hspace{.25em}
\subfloat[$w(\bm{x})  = .5 \cos(3\pi x)\cos(3\pi y)\cos(3\pi z) $]{\includegraphics[width=.35\textwidth]{figs/pplanew0.png}}
\caption{Mesh and $xz$, $xy$ slices of $\bm{v}_1$ at $T = .5$.  The order of approximation is taken to be $N=5$.  }
\label{fig:3d}
\end{figure}
Figure~\ref{fig:3d} shows the $x$-velocity of the computed solution at $T = .5$ with
\[
w(\bm{x}) = .5 \cos(3\pi x)\cos(3\pi y)\cos(3\pi z), 
\]  
as well as $w(\bm{x}) = 0$ for reference.  Figure~\ref{subfig:mesh} shows the unstructured mesh of 222824 tetrahedral elements of degree $N=5$ used to compute both solutions.

@@

We note that the implementation of this method reduces to the application of the weight-adjusted mass matrix inverse and the evaluation of constant-coefficient terms in the DG formulation.  The cost of the latter step can be reduced (especially at high orders of approximation) by using fast methods based on Bernstein-Bezier bases for the application of derivative and lift matrices for constant-coefficient terms \cite{chan2015bbdg}.  %Finally, the approach presented here is more generally applicable to problems involving a weighted mass matrix with a matrix-valued weight, including hyperbolic systems of PDEs with a left hand side of the form $\bm{A}_{0}(\bm{x})\pd{\bm{U}}{t}$, such as Maxwell's equations for cloaking problems \cite{li2012time}.
